\documentclass{article}
\usepackage[utf8]{inputenc}

 
\begin{document}
\subsection{{Introduction}}
Bangladesh is a populous country. Bangladesh ranks seventh in the world in terms of population. According to the 
Department of Youth Development, about one third of this population or 53 million is the youth population.Although the 
country’s GDP has increased over the years,with growing youth population, struggles continue for job seekers to find their 
desired jobs, resulting in the rise of unemployment.Among other reasons, one cause is the lack of knowledge about job 
availability, which is hindering employment opportunities.With job applications like LINKEDIN, UPWORK and SHEBAXYZ 
already there on the market, the problem to find the most desirable job opportunities still remains.So how is our job portal 
any different from all the existing applications and portals? Well our goal for this project is to create such a web application 
which will not only be more user friendly but the job seekers will find all different sorts of job listings under one 
umbrella.Starting from regular jobs which is educational based, part- time full - time and internships, to contractual jobs and 
even day - to - day jobs e.g. plumbing, delivery man etc our platform will connect with every type of job seeking individuals 
across the country.
      
\subsection{ \textbf{  OBJECTIVE }}
 
\begin{itemize}
\item More user friendly 
\end{itemize}
             
\begin{itemize}
\item All types of jobs under one roof
\end{itemize}
\begin{itemize}
\item Recruiters get a very detailed description of employees through their profile
\item Endorsements for job seekers for regular jobs
\item Rating system for contractual and day - to - day jobs 
\item Searching - Age, Experience and Location based searching
\item Opportunity for job seekers to share their work skill in their profile through uploading videos.
\end{itemize}
\subsection{   \textbf{Target Customer:}
}
\begin{itemize}
\item \textbf{Job-SEEKERS} -  Starting from day - to - day job seekers like plumbers , electricians, to contractual job seekers like 
photographers, illustrators, freelancers to regular job seekers like managers , CEO, etc.
\end{itemize}

\begin{itemize}
\item \textbf{RECRUITERS }: All types of companies and customers looking to employ people from various line of work and various expertise.
\end{itemize}
 
\subsection{Value Proposition}
Our job seeking portal can bring key benefits to the persons of all
stages working out there in our society. The job providers will not 
have to go to the person to person for hiring, this website will 
reduce the time and bothering. One can reach a bigger audience 
through this website, also it’s cost-effective/flexible and 
immediate as well as job provider can hire someone from 
anywhere and anytime. One can discuss about payments or costs 
without talking in person. It allows confidentiality, expedites 
hiring process besides it’s accessible for all the job seekers and 
providers. After all, the most efficient thing is, it’s simple and 
easy for everyone.
\subsection{Web Application Feature and description}
If someone access the domain, first there will be a 
homepage where one can see two options; one for the job 
providers and another one for the job seekers.
If anyone searching for jobs he/she will select job seeking 
option. Next, he/she will have to sign up a form with 
his/her own information as well as qualifications. Once 
account is created he/she can :

• Search for suitable job.

• See jobs provided with necessary informations.

• Apply for the jobs.

• Decline applied jobs before confirmation.

• Discuss with the job providers about the payment 
    methods or any job   related topics.

• Add his/her before worked projects to his/her profile 
   for the viewers.
\begin{itemize}
\item Give feedback.
\end{itemize}

• Check all completed works from his history tab.


• Select ‘Work Completed’ option when the work is 
   done.
\subsection{For the job providers they will also have to create an 
account through the job providers option. After creating 
account he/she can :}
• Search for perfect candidates for the job.

• Select someone for the job.

• Discuss about the job and payment methods.

• Provide job completing time.

• Give ratings and suggestions.

• Check job seekers completed works from his/her 
profile.

• Give feedback.

• Get notification if the work is done.
\subsection{If the job is any type of physical activity related jobs which 
will have to complete in person (such as electricians, 
plumbers etc. work in person), then :}

• The job provider and job seeker will have to fill up a
dealing agreement and policy form in the website.• They will have to fill up a non-cancellation agreement 
after the job is confirmed, which means they will not 
be able to decline the job once it is confirmed after 
discussion
\subsection{Tools and Resources}
\begin{itemize}
\item HTML
\end{itemize}
\begin{itemize}
\item MySQL
\end{itemize}
\begin{itemize}
\item PHP
\end{itemize}
\begin{itemize}
\item Web server
\end{itemize}
\subsection{Challenges:}
One of the biggest challenges can be the cost management. As huge amount of data will be there like image , job seekers info .So there is a chance of huge cost to ensure data security .The second challenge is to ensure authenticity of data.The next important aspect and challenge of the creation of this site is browsing compatibility. We need to check it on different browsers, operating systems and monitor resolutions among others.Also providing secured connection will
be difficult
\end{document}
